Convex Surrogates via Polyhedral Losses

### 2019-01-31 cvx-fin.tex
moving notation before the section, and progress.

@@

We study the minimization of \emph{loss functions} of the form $\ell: \R \to \reals^{\Y}_+$.
The abstract set $\R$ is the \emph{report space}, $\ell(r)$ is a vector specifying the loss of report $r$ on all outcomes, and $\ell(r)_y \in \reals_+$ is the loss of $r$ when outcome $y$ is observed.
The expected loss of report $r$ when $y \sim p$ is written $\langle p, \ell(r) \rangle$.

>>>>

\newcommand{\Ind}{\mathbf{1}}

@@

We study the minimization of \emph{loss functions} of the form $\ell: \R \to \reals^{\Y}_+$.
The abstract set $\R$ is the \emph{report space}, $\ell(r)$ is a vector specifying the loss of report $r$ on all outcomes, and $\ell(r)_y \in \reals_+$ is the loss of $r$ when outcome $y$ is observed.
The expected loss of report $r$ when $y \sim p$ is written $\langle p, \ell(r) \rangle$.
For example, the $0-1$ loss has $\R = \Y$ with $\ell(r)_y = \Ind[r \neq y]$.

A \emph{property} formally captures the relationship between distributions $p$ and minimizers of expected loss.
In this paper, we will use double arrow notation to mean a mapping to all nonempty subsets.
So the notation $\gamma: \simplex \toto \R$ is shorthand for $\gamma: \simplex \to 2^{\R} \setminus \emptyset$.

\begin{definition}

\end{definition}
